Outline

### 2021-01-05 text/main.Rmd
edits

**Authors:** Nina M. D. Schiettekatte^1,2,*^, Simon J. Brandl^3^, Jordan M. Casey^3^, Nicholas A. J. Graham^4^, Diego R. Barneche^5,6^, Deron E. Burkepile^7,8^, Jacob E. Allgeier^9^, Jesús E. Arias-Gonzaléz^10^, Graham J. Edgar^11^, Carlos E. L. Ferreira^12^, Sergio R. Floeter^13^, Alan M. Friedlander^14^, Alison L. Green^15^, Michel Kulbicki^2,16^, Yves Letourneur^2,17^, Osmar J. Luiz^18^, Alexandre Mercière^1,2^, Fabien Morat^1,2^, Katrina S. Munsterman^9^, Enrico L. Rezende^19^, Fabian A. Rodríguez‐Zaragoza^20^, Rick D. Stuart-Smith^11^, Laurent Vigliola^2,16^, Sébastien Villéger^21^, Valeriano Parravicini^1,2^

^1^PSL Université Paris: EPHE-UPVD-CNRS, USR 3278 CRIOBE, Université de Perpignan, Perpignan, France;    
^2^Laboratoire d'Excellence “CORAIL”, Perpignan, France;     
^3^The University of Texas at Austin, Marine Science Institute, Port Aransas, TX 78373, USA;      
^4^Lancaster Environment Centre, Lancaster University, Lancaster, LA1 4YQ, UK;      
^5^Australian Institute of Marine Science, Crawley, WA, Australia;      
^6^Oceans Institute, The University of Western Australia, Crawley, WA, Australia;      
^7^Department of Ecology, Evolution, and Marine Biology, University of California, Santa Barbara, CA, USA;      
^8^Marine Science Institute, University of California, Santa Barbara, CA, USA;      
^9^Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, MI, USA;      
^10^Laboratorio Ecología de Ecosistemas de Arrecifes Coralinos, Departamento Recursos del Mar, CINVESTAV Unidad Mérida, AP73 Cordemex, CP97310, Mérida, Yucatán, Mexico;      
^11^Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, TAS, Australia;      
^12^Departamento de Biologia Marinha, Universidade Federal Fluminense (UFF), Niterói,  the state of Rio de Janeiro (RJ), Brazil;     
^13^Marine Macroecology and Biogeography Lab, Depto. de Ecologia e Zoologia, CCB, Universidade Federal de Santa Catarina, Florianopolis, Santa Catarina, Brazil;      
^14^Department of Biology, University of Hawaii, Honolulu, HI, USA;      
^15^Red Sea Research Center, King Abdullah University of Science and Technology, Thuwal 23955-6900, Saudi Arabia;
^16^Institut de Recherche pour le Développement, UMR UR-IRD-CNRS-IFREMER-UNC ENTROPIE, Nouméa, New Caledonia, France;     
^17^Université de la Nouvelle-Calédonie, UMR UR-IRD-CNRS-IFREMER-UNC ENTROPIE, Nouméa, New Caledonia, France;     
^18^Research Institute for the Environment and Livelihoods, Charles Darwin University, Darwin, Australia;     
^19^Departamento de Ecología, Center of Applied Ecology and Sustainability (CAPES), Facultad de Ciencias Biológicas, Pontificia Universidad Católica de Chile, Santiago 6513677, Chile;      
^20^Laboratorio de Ecosistemas Marinos y Acuicultura (LEMA), Departamento de 12 Ecología, CUCBA, Universidad de Guadalajara. México. Carr. Guadalajara-Nogales 13 km. 15.5, Las Agujas Nextipac, Zapopan, C.P. 45110, Jalisco, 14, Mexico;     
^21^MARBEC, Université de Montpellier, CNRS, IFREMER, IRD, Montpellier, France     
^*^Correspondance to NMDS (nina.schiettekatte@gmail.com).

@@

@@

**Main Text:** 
The flow of elements through biological communities fuels all life on Earth [@Welti2017]. Preserving these fluxes, often termed ecosystem functions, is critical for the integrity of ecosystems [@Welti2017].
For millennia, resources have been managed with an economic mindset to maximize desirable functions such as the production of plant or animal biomass [@Weisser2017].
Sustaining multiple functions likely requires both high species richness and a variety of species assemblages across a landscape [@Zavaleta2010].
However, in agro-ecological settings, efforts to maximize one function negatively impact another (e.g. timber production vs. erosion control), shedding light on the existence of trade-offs between functions [@Tallis2008; @Zavaleta2010].
An understanding of such trade-offs is required to make informed management decisions [@Rodriguez2006], but simultaneously quantifying multiple ecosystem functions is challenging.
Therefore, trade-offs between functions, their drivers, and functional vulnerability are poorly understood in many ecosystems [@Brandl2019front].

@@

Here, we integrate biogeochemistry and community ecology to advance our understanding of the elemental fluxes that underpin reef fish functioning.
Using empirically-collected species-specific data on basic organismal processes and Bayesian phylogenetic models to extrapolate to species that lack data, we parameterize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory (daily consumption of primary producers, expressed as mass of carbon), and piscivory (daily consumption of fishes, expressed as mass of carbon).
We apply these bioenergetic models to all individuals across 9,118 reef fish communities in 585 sites worldwide (Extended Data Table 1) to:
(1) quantify community-level reef fish functions and their trade-offs,
(2) extract the community- and species-level effects on these functions, and
(3) gauge the vulnerability of reef fish functioning in the Anthropocene.

The five key ecosystem functions performed by fishes across the world's reefs exhibit high variability (Fig. 1).
Biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front], and as can be expected from the cumulative nature of community-level ecosystem functioning, we indeed observed a strong relationship between fish standing stock biomass and all five functions (Extended Data Fig. 1a-e, Extended Data Fig. 2).
However, our analyses demonstrate that reef fish functions vary remarkably  after accounting for biomass, as functions of communities with similar biomass may differ with two orders of magnitude and a two-fold difference in biomass can yield similar levels for functions (i.e. biomass production, Extended Data Fig. 1a-f).
Thus, using biomass as a sole proxy for functioning can mask differences in critical community-level functions.
Further, we demonstrate strong trade-offs among the five functions, independent of biomass (Fig.1, Extended Data Fig. 1g).
For example, high herbivory rates or nitrogen excretion negatively correlate with rates of phosphorus excretion.
As a consequence, for a given value of standing stock biomass, no reef can yield above average values across all five functions.
In other words, while many reefs may stand out as hotspots for one function, none can maximize functioning as a holistic, multifaceted concept (Fig. 1).

Community structure and species-specific traits clearly impact rates of functioning. 
First, using community-level ecological predictors known to affect elemental fluxes [@Schiettekatte2020] (body size, trophic level, species richness, biomass, temperature, and age structure; Fig. 2), we show that correlations between functions are mediated by contrasting aspects of community structure (Fig. 2; Extended Data Table 2; Extended Data Fig. 2).
For example, phosphorus excretion is higher in communities with many large-bodied, mature fishes that occupy high trophic levels, thus creating a positive relationship between phosphorus excretion and piscivory (Extended Fig. 1g; See @Allgeier2014).
In contrast, biomass production is highest in communities dominated by small and/or immature fishes at low trophic levels, creating a trade-off between biomass production and phosphorus excretion.
Metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportional contributions to functions that rely on rapid energetic turnover [@Barneche2018; @Morais2020glob; @Brandl2019science].
Conversely, fishes in early life stages or with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions of these individuals to phosphorus excretion.
Thus, due to variations in organismal physiology and life-history traits [@Schiettekatte2020; @Allgeier2016], fish community structure can significantly impact ecosystem-wide functioning [@Schramski2015].

Secondly, alongside features of community structure, ecosystem functioning may also be influenced by specific high-performing taxa. 
Certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass or due to specific characteristics (Fig. 3a; Extended Data Fig. 3,4). 
Further, abundant species can impact rates of functioning at the community level [@Ruttenberg2019; @Topor2019].
Therefore, we assessed the role of each species by quantifying their relative contributions and the degree to which they disproportionally induce (i.e. dominate) different functions in each community.
We show that functions consistently hinge a few dominant species (Fig. 3b). Specifically, more than 50% of a given function, on average, is upheld by only 12% of the species present within a local community.
However, the identity of these species varies dramatically (Fig. 3c), despite evidence for some species assuming key functional roles across widely-dispersed locations [@Bellwood2003].
While few high-performing taxa dominate functioning in each location, there are almost no species that are important across their entire range, and most species are locally important in at least one community.
Indeed, 70% of all species contributed disproportionally to a specific function in at least one reef fish community.
Despite high species richness on coral reefs, researchers often report the existence of functionally-dominant “key species” [e.g. @Bellwood2006].
Our results reveal that while functional dominance is indeed prevalent, the identity of local, dominant species vary strongly across different locations, suggesting that maintaining high levels of species richness across coral reef regions is essential to sustain global ecosystem functioning [@Topor2019].

@@

![Figure 2: Fixed effect values from Bayesian linear regressions that examine the effects of community variables on five functions. Community variables include species richness, and descriptors of the trophic level, size, and immaturity of fishes. To represent both the median and the spread of trophic level, size, and immaturity across individuals inside a community, we included lower and upper 95% quantile values of these three traits as community variables. All data were log-transformed and standardized to compare across functions and variables (see Extended Data Table 2 for parameter values on non-standardized data). Dots represent the average effect size estimate, and horizontal lines indicate the 95% credible interval.](../output/plots/fig2_com_slopes.png)

@@

# References

>>>>

**Authors:** Nina M. D. Schiettekatte^1,2\*^, Simon J. Brandl^3^, Jordan M. Casey^3^, Nicholas A. J. Graham^4^, Diego R. Barneche^5,6^, Deron E. Burkepile^7,8^, Jacob E. Allgeier^9^, Jesús E. Arias-Gonzaléz^10^, Graham J. Edgar^11^, Carlos E. L. Ferreira^12^, Sergio R. Floeter^13^, Alan M. Friedlander^14^, Alison L. Green^15^, Michel Kulbicki^2,16^, Yves Letourneur^2,17^, Osmar J. Luiz^18^, Alexandre Mercière^1,2^, Fabien Morat^1,2^, Katrina S. Munsterman^9^, Enrico L. Rezende^19^, Fabian A. Rodríguez‐Zaragoza^20^, Rick D. Stuart-Smith^11^, Laurent Vigliola^2,16^, Sébastien Villéger^21^, Valeriano Parravicini^1,2^

**Affiliations:**     
^1^PSL Université Paris: EPHE-UPVD-CNRS, USR 3278 CRIOBE, Université de Perpignan, Perpignan, France;    
^2^Laboratoire d'Excellence “CORAIL”, Perpignan, France;     
^3^The University of Texas at Austin, Marine Science Institute, Port Aransas, TX 78373, USA;      
^4^Lancaster Environment Centre, Lancaster University, Lancaster, LA1 4YQ, UK;      
^5^Australian Institute of Marine Science, Crawley, WA, Australia;      
^6^Oceans Institute, The University of Western Australia, Crawley, WA, Australia;      
^7^Department of Ecology, Evolution, and Marine Biology, University of California, Santa Barbara, CA, USA;      
^8^Marine Science Institute, University of California, Santa Barbara, CA, USA;      
^9^Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, MI, USA;      
^10^Laboratorio Ecología de Ecosistemas de Arrecifes Coralinos, Departamento Recursos del Mar, CINVESTAV Unidad Mérida, AP73 Cordemex, CP97310, Mérida, Yucatán, Mexico;      
^11^Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, TAS, Australia;      
^12^Departamento de Biologia Marinha, Universidade Federal Fluminense (UFF), Niterói,  the state of Rio de Janeiro (RJ), Brazil;     
^13^Marine Macroecology and Biogeography Lab, Depto. de Ecologia e Zoologia, CCB, Universidade Federal de Santa Catarina, Florianopolis, Santa Catarina, Brazil;      
^14^Department of Biology, University of Hawaii, Honolulu, HI, USA;      
^15^Red Sea Research Center, King Abdullah University of Science and Technology, Thuwal 23955-6900, Saudi Arabia;
^16^Institut de Recherche pour le Développement, UMR UR-IRD-CNRS-IFREMER-UNC ENTROPIE, Nouméa, New Caledonia, France;     
^17^Université de la Nouvelle-Calédonie, UMR UR-IRD-CNRS-IFREMER-UNC ENTROPIE, Nouméa, New Caledonia, France;     
^18^Research Institute for the Environment and Livelihoods, Charles Darwin University, Darwin, Australia;     
^19^Departamento de Ecología, Center of Applied Ecology and Sustainability (CAPES), Facultad de Ciencias Biológicas, Pontificia Universidad Católica de Chile, Santiago 6513677, Chile;      
^20^Laboratorio de Ecosistemas Marinos y Acuicultura (LEMA), Departamento de 12 Ecología, CUCBA, Universidad de Guadalajara. México. Carr. Guadalajara-Nogales 13 km. 15.5, Las Agujas Nextipac, Zapopan, C.P. 45110, Jalisco, 14, Mexico;     
^21^MARBEC, Université de Montpellier, CNRS, IFREMER, IRD, Montpellier, France     
^\*^Correspondance to Nina M. D. Schiettekatte (nina.schiettekatte@gmail.com)

@@

\newpage

@@

\newpage
**Main Text:** 
The flow of elements through biological communities fuels all life on Earth [@Welti2017]. Preserving these fluxes, often termed ecosystem functions, is critical for the integrity of ecosystems [@Welti2017].
For millennia, resources have been managed with an economic mindset to maximize desirable functions such as the production of plant or animal biomass [@Weisser2017].
Sustaining multiple functions likely requires both high species richness and a variety of species assemblages across a landscape [@Zavaleta2010].
However, in agro-ecological settings, efforts to maximize one function negatively impact another (e.g. timber production vs. erosion control), shedding light on the existence of trade-offs between functions [@Tallis2008; @Zavaleta2010].
An understanding of such trade-offs is required to make informed management decisions [@Rodriguez2006], but simultaneously quantifying multiple ecosystem functions is challenging.
Therefore, trade-offs between functions, their drivers, and functional vulnerability are poorly understood in many ecosystems [@Brandl2019front].

@@

Here, we integrate biogeochemistry and community ecology to advance our understanding of the elemental fluxes that underpin reef fish functioning.
Using empirically-collected species-specific data on basic organismal processes and Bayesian phylogenetic models to extrapolate to species that lack data, we parameterize individual-level bioenergetic models to estimate five key ecosystem functions: nitrogen (N) excretion, phosphorus (P) excretion, biomass production, herbivory (daily consumption of primary producers, expressed as mass of carbon), and piscivory (daily consumption of fishes, expressed as mass of carbon).
We apply these bioenergetic models to all individuals across 9,118 reef fish communities in 585 sites worldwide (Table S1) to:
(1) quantify community-level reef fish functions and their trade-offs,
(2) extract the community- and species-level effects on these functions, and
(3) gauge the vulnerability of reef fish functioning in the Anthropocene.

The five key ecosystem functions performed by fishes across the world's reefs exhibit high variability (Fig. 1).
Biomass is the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front], and as can be expected from the cumulative nature of community-level ecosystem functioning, we indeed observed a strong relationship between fish standing stock biomass and all five functions (Fig. S1a-e, Fig. S2).
However, our analyses demonstrate that reef fish functions vary remarkably  after accounting for biomass, as functions of communities with similar biomass may differ with two orders of magnitude and a two-fold difference in biomass can yield similar levels for functions (i.e. biomass production, Fig. S1a-f).
Thus, using biomass as a sole proxy for functioning can mask differences in critical community-level functions.
Further, we demonstrate strong trade-offs among the five functions, independent of biomass (Fig.1, Fig. S1g).
For example, high herbivory rates or nitrogen excretion negatively correlate with rates of phosphorus excretion.
As a consequence, for a given value of standing stock biomass, no reef can yield above average values across all five functions.
In other words, while many reefs may stand out as hotspots for one function, none can maximize functioning as a holistic, multifaceted concept (Fig. 1).

Community structure and species-specific traits clearly impact rates of functioning. 
First, using community-level ecological predictors known to affect elemental fluxes [@Schiettekatte2020] (body size, trophic level, species richness, biomass, temperature, and age structure; Fig. 2), we show that correlations between functions are mediated by contrasting aspects of community structure (Fig. 2; Table S2; Fig. S2).
For example, phosphorus excretion is higher in communities with many large-bodied, mature fishes that occupy high trophic levels, thus creating a positive relationship between phosphorus excretion and piscivory (Fig S1g; See @Allgeier2014).
In contrast, biomass production is highest in communities dominated by small and/or immature fishes at low trophic levels, creating a trade-off between biomass production and phosphorus excretion.
Metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportional contributions to functions that rely on rapid energetic turnover [@Barneche2018; @Morais2020glob; @Brandl2019science].
Conversely, fishes in early life stages or with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions of these individuals to phosphorus excretion.
Thus, due to variations in organismal physiology and life-history traits [@Schiettekatte2020; @Allgeier2016], fish community structure can significantly impact ecosystem-wide functioning [@Schramski2015].

Secondly, alongside features of community structure, ecosystem functioning may also be influenced by specific high-performing taxa. 
Certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass or due to specific characteristics (Fig. 3a; Fig. S3,S4). 
Further, abundant species can impact rates of functioning at the community level [@Ruttenberg2019; @Topor2019].
Therefore, we assessed the role of each species by quantifying their relative contributions and the degree to which they disproportionally induce (i.e. dominate) different functions in each community.
We show that functions consistently hinge a few dominant species (Fig. 3b). Specifically, more than 50% of a given function, on average, is upheld by only 12% of the species present within a local community.
However, the identity of these species varies dramatically (Fig. 3c), despite evidence for some species assuming key functional roles across widely-dispersed locations [@Bellwood2003].
While few high-performing taxa dominate functioning in each location, there are almost no species that are important across their entire range, and most species are locally important in at least one community.
Indeed, 70% of all species contributed disproportionally to a specific function in at least one reef fish community.
Despite high species richness on coral reefs, researchers often report the existence of functionally-dominant “key species” [e.g. @Bellwood2006].
Our results reveal that while functional dominance is indeed prevalent, the identity of local, dominant species vary strongly across different locations, suggesting that maintaining high levels of species richness across coral reef regions is essential to sustain global ecosystem functioning [@Topor2019].

@@

![Figure 2: Fixed effect values from Bayesian linear regressions that examine the effects of community variables on five functions. Community variables include species richness, and descriptors of the trophic level, size, and immaturity of fishes. To represent both the median and the spread of trophic level, size, and immaturity across individuals inside a community, we included lower and upper 95% quantile values of these three traits as community variables. All data were log-transformed and standardized to compare across functions and variables (see Table S2 for parameter values on non-standardized data). Dots represent the average effect size estimate, and horizontal lines indicate the 95% credible interval.](../output/plots/fig2_com_slopes.png)

@@

<br>

**References and Notes:**         
<div id="refs"></div>

**Acknowledgements:** 
We thank the staff at CRIOBE, Moorea for field support. We would also like to thank Jérémy Carlot, Beverly French, Titouan Roncin, Yann Lacube, Camille Gache, Gabrielle Martineau, Kailey Bissell, Benoit Espiau, Calvin Quigley, Kaitlyn Landfield and Tommy Norin for their help in the field, Sophie Schiettekatte for proof-reading the manuscript, and Guillemette de Sinéty and Jérémy Wicquart for their contribution to otolith analyis.
**Funding:** 
This research was funded by the BNP Paribas Foundation (Reef Services Project) and the French National Agency for Scientific Research (ANR; REEFLUX Project; ANR‐17‐CE32‐0006). This research is product of the SCORE-REEF group funded by the Centre de Synthèse et d’Analyse sur la Biodiversité (CESAB) of the Foundation pour la Recherche sur la Biodiversité (FRB) and the Agence Nationale de la Biodiversité (AFB). VP was supported by the Institut Universitaire de France (IUF) and JMC was supported by a Make Our Planet Great Again Postdoctoral Grant (mopga‐pdf‐0000000144).
**Author contributions:** 
NMDS and VP conceived the idea and NMDS, VP, SJB, and JMC designed methodology; NMDS, JMC, SJB, AM, FM, VP, KSM, JEA and DEB collected the data; All authors shared existing data. NMDS analyzed the data and led the writing of the manuscript. All authors contributed significantly to the drafts and approved the final version for publication.
**Competing interests:** None declared.
**Data and materials availability:** 
All data and code to reproduce figures are available online through GitHub (https://github.com/nschiett/global_proc) and figshare (https://figshare.com/s/f789aec2c20492c4f0f9). All data on individual fish traits are available from the corresponding author on reasonable request.

**Supplementary Materials:**
Materials and Methods     
Figures S1-S5     
Table S1     
Supplementary methods     
References (##-##)

### 2021-01-05 text/methods.Rmd
edits

## 2. Bioenergetic modeling
\noindent Here, we focused on 5 key processes mediated by fish: N excretion rate (gN/day/m^2^), P excretion rate (gP/day/m^2^), production of body mass through growth (gC/day/m^2^), herbivory, i.e. ingestion rate of macrophytes (gC/day/m^2^), and piscivory, i.e. ingestion rate of fishes (g/day/m^2^). These 5 processes were estimated in each transect using individual-based bioenergetic models that predicts elemental fluxes, including ingestion rate, excretion rates of N and P, and growth rate.
The bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020]. We quantified the input parameters, including elements of metabolism, growth, and diet and body stoichiometry, for all 1110 species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (See supplementary methods). We ran the model for each combination of species identity, body size, and sea surface temperature (n = 30668) to get the contribution of each individual to each process in each transect and the cumulated estimates for the fish community per surface area. Each process is thus expressed in dry mass per day per square meter. We note that N excretion, P excretion, and biomass production include contributions of all fishes, whereas herbivory and piscivory are carried out by a subset of the community, with respect to their trophic guild [@Parravicini2020]. To reduce the occurrence of misclassification of herbivores and piscivores, we categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds for a global fish species database that defines trophic guilds based on empirical data using a quantitative, unbiased, and fully reproducible framework [@Parravicini2020]. Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on expert opinion [@Mouillot2014; @Parravicini2020] (Extended data figure 5). Both the herbivory and piscivory rates are congruent with the expert opinion trophic guild classifications.

>>>>

## 2. Bioenergetic modeling
\noindent Here, we focused on 5 key processes mediated by fish: N excretion rate (gN/day/m^2^), P excretion rate (gP/day/m^2^), production of body mass through growth (gC/day/m^2^), herbivory, i.e. ingestion rate of macrophytes (gC/day/m^2^), and piscivory, i.e. ingestion rate of fishes (g/day/m^2^). These 5 processes were estimated in each transect using individual-based bioenergetic models that predicts elemental fluxes, including ingestion rate, excretion rates of N and P, and growth rate.
The bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020]. We quantified the input parameters, including elements of metabolism, growth, and diet and body stoichiometry, for all 1110 species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (See supplementary methods). We ran the model for each combination of species identity, body size, and sea surface temperature (n = 30668) to get the contribution of each individual to each process in each transect and the cumulated estimates for the fish community per surface area. Each process is thus expressed in dry mass per day per square meter. We note that N excretion, P excretion, and biomass production include contributions of all fishes, whereas herbivory and piscivory are carried out by a subset of the community, with respect to their trophic guild [@Parravicini2020]. To reduce the occurrence of misclassification of herbivores and piscivores, we categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds for a global fish species database that defines trophic guilds based on empirical data using a quantitative, unbiased, and fully reproducible framework [@Parravicini2020]. Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on expert opinion [@Mouillot2014; @Parravicini2020] (Fig. S5). Both the herbivory and piscivory rates are congruent with the expert opinion trophic guild classifications.

### 2021-01-05 text/suppl_methods.Rmd
last edits text before submission to nature
edits

To apply the bioenergetic model that estimates fluxes of carbon (C), nitrogen (N), and phosphorus (P), a number of parameters are required [see @Schiettekatte2020]. Here, we describe how these parameters were quantified for all 1110 species in our database, with a combination of literature, empirical measures, and Bayesian models. All analyzes were carried out in R v.3.6.3 and Bayesian modes were run using Stan [@Carpenter2017] and the R package brms [@Burkner2017].

@@

\noindent The CNP\% content of organisms is known to be highly conserved within families (REF). We therefore use phylogeny to extrapolate these values. We fitted C, N and P contents (\%) through a hierarchical phylogenetic multivariate normal model with phylogenetic effects and random effects per species.

>>>>

To apply the bioenergetic model that estimates fluxes of carbon (C), nitrogen (N), and phosphorus (P), a number of parameters are required [see @Schiettekatte2020]. Here, we describe how these parameters were quantified for all 1110 species in our database, with a combination of literature, empirical measures, and Bayesian models. All protocols related to the capture and handling of fish complied to the ethical standards of CRIOBE and EPHE, and the University of California Santa Barbara’s Institutional Animal Care and Use Committee (IACUC #915 2016-2019). Extraction and transport of samples were approved by the government of French Polynesia. All analyzes were carried out in R v.3.6.3 and Bayesian modes were run using Stan [@Carpenter2017] and the R package brms [@Burkner2017].

@@

\noindent The CNP\% content of organisms is known to be highly conserved within families [@Allgeier2020sci]. We therefore use phylogeny to extrapolate these values. We fitted C, N and P contents (\%) through a hierarchical phylogenetic multivariate normal model with phylogenetic effects and random effects per species.
